My title\thanks{Code and data are available at: \url{https://github.com/RohanAlexander/starter_folder}.}

### 2024-11-14 paper/paper.tex
Updated code chunk 8

\title{My title\thanks{Code and data are available at:
\url{https://github.com/RohanAlexander/starter_folder}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Another author}
\date{November 13, 2024}

@@

For this study, we utilize data from Project Hammer, a Canadian
initiative designed to monitor grocery prices across major retailers in
Canada. The Project Hammer dataset was collected from eight prominent
Canadian grocery vendors---Voila, T\&T, Loblaws, No Frills, Metro,
Galleria, Walmart, and Save-On-Foods---between February 28, 2024, and
the latest available data load in the database
(\textbf{citeProjectHammerData?}). This dataset enables us to
investigate price fluctuations, identify pricing trends, and explore
potential competitive or collusive patterns within the Canadian grocery
sector. Project Hammer aims to support regulatory efforts by providing
data on price transparency, making it suitable for academic research and
potential legal analysis. Following data processing and cleaning
procedures outlined in Section 3.2, the dataset was structured to allow
an analysis of historical price changes and vendor-specific price
patterns. The dataset contains 1,996,969 rows and 5 columns, with
variables capturing product (product name), vendor\_name (name of the
grocery retailer), price\_current (current product price at the time of
recording), price\_old (previous recorded price for the product), and
price\_difference (difference between the current and old prices). Price
data is recorded in Canadian dollars and captures a broad range of
grocery items from various categories, including fresh produce, dairy,
pantry staples, and household items. To ensure the quality and
consistency of the data, we focused on removing missing values and
imputing outlier prices when necessary. For this analysis, we excluded
entries with extreme price fluctuations beyond three standard
deviations, as these could represent temporary discounts or data
recording anomalies. This cleaning process provides a balanced and
accurate reflection of grocery pricing, allowing for robust statistical
analysis on vendor-specific trends and average price comparisons across
product types. By narrowing the scope to recent data, Project Hammer's
dataset captures real-time fluctuations in grocery pricing, providing
timely insights into potential market dynamics and consumer price
impacts. The analysis allows for future investigation of temporal price
trends, vendor-based price differences, and, more broadly, consumer
affordability in a market facing rising cost-of-living pressures.

@@

\begin{itemize}
    \item $\beta_0$ is the intercept term, representing the baseline estimage of `price_current`
    \item $\beta_1$, $\beta_2$, and $\beta_3$ are the coefficients representing the effects of `price_old`, `vendor_name` and `price_difference` on `price_current`.
    \item $\sigma^2$represents the variance of the error term, capturing unexplained variability in current prices.
\end{itemize}

@@

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\#\#\# Read data \#\#\#\#}
\CommentTok{\# Load the cleaned data with data.table for efficiency}
\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{fread}\NormalTok{(}\StringTok{"C:/Users/eliza/Downloads/hammer{-}3{-}compressed/cleaned\_price\_changes.csv"}\NormalTok{)}

\CommentTok{\# Split data into training and testing sets}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{853}\NormalTok{)}
\NormalTok{train\_indices }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{seq\_len}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(analysis\_data)), }\AttributeTok{size =} \FloatTok{0.8} \SpecialCharTok{*} \FunctionTok{nrow}\NormalTok{(analysis\_data))}
\NormalTok{analysis\_data\_train }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data[train\_indices]}
\NormalTok{analysis\_data\_test }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data[}\SpecialCharTok{{-}}\NormalTok{train\_indices]}
\DocumentationTok{\#\#\# Model data \#\#\#\#}
\CommentTok{\# Define a Bayesian regression model to predict \textasciigrave{}price\_current\textasciigrave{}}

\DocumentationTok{\#\#\# Model data \#\#\#\#}
\CommentTok{\# Define a Bayesian regression model to predict \textasciigrave{}price\_current\textasciigrave{}}
\NormalTok{model }\OtherTok{\textless{}{-}} \FunctionTok{stan\_glm}\NormalTok{(}
  \AttributeTok{formula =}\NormalTok{ price\_current }\SpecialCharTok{\textasciitilde{}}\NormalTok{ price\_old }\SpecialCharTok{+} \FunctionTok{as.factor}\NormalTok{(vendor\_name) }\SpecialCharTok{+}\NormalTok{ price\_difference,}
  \AttributeTok{data =}\NormalTok{ analysis\_data\_train,}
  \AttributeTok{family =} \FunctionTok{gaussian}\NormalTok{(),}
  \AttributeTok{prior =} \FunctionTok{normal}\NormalTok{(}\AttributeTok{location =} \DecValTok{0}\NormalTok{, }\AttributeTok{scale =} \FloatTok{2.5}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),}
  \AttributeTok{prior\_intercept =} \FunctionTok{normal}\NormalTok{(}\AttributeTok{location =} \DecValTok{0}\NormalTok{, }\AttributeTok{scale =} \FloatTok{2.5}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),}
  \AttributeTok{prior\_aux =} \FunctionTok{exponential}\NormalTok{(}\AttributeTok{rate =} \DecValTok{1}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),}
  \AttributeTok{seed =} \DecValTok{853}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 1).
Chain 1: 
Chain 1: Gradient evaluation took 0.001214 seconds
Chain 1: 1000 transitions using 10 leapfrog steps per transition would take 12.14 seconds.
Chain 1: Adjust your expectations accordingly!
Chain 1: 
Chain 1: 
Chain 1: Iteration:    1 / 2000 [  0%]  (Warmup)
Chain 1: Iteration:  200 / 2000 [ 10%]  (Warmup)
Chain 1: Iteration:  400 / 2000 [ 20%]  (Warmup)
Chain 1: Iteration:  600 / 2000 [ 30%]  (Warmup)
Chain 1: Iteration:  800 / 2000 [ 40%]  (Warmup)
Chain 1: Iteration: 1000 / 2000 [ 50%]  (Warmup)
Chain 1: Iteration: 1001 / 2000 [ 50%]  (Sampling)
Chain 1: Iteration: 1200 / 2000 [ 60%]  (Sampling)
Chain 1: Iteration: 1400 / 2000 [ 70%]  (Sampling)
Chain 1: Iteration: 1600 / 2000 [ 80%]  (Sampling)
Chain 1: Iteration: 1800 / 2000 [ 90%]  (Sampling)
Chain 1: Iteration: 2000 / 2000 [100%]  (Sampling)
Chain 1: 
Chain 1:  Elapsed Time: 0.56 seconds (Warm-up)
Chain 1:                225.422 seconds (Sampling)
Chain 1:                225.982 seconds (Total)
Chain 1:

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 2).
Chain 2: 
Chain 2: Gradient evaluation took 3.6e-05 seconds
Chain 2: 1000 transitions using 10 leapfrog steps per transition would take 0.36 seconds.
Chain 2: Adjust your expectations accordingly!
Chain 2: 
Chain 2: 
Chain 2: Iteration:    1 / 2000 [  0%]  (Warmup)
Chain 2: Iteration:  200 / 2000 [ 10%]  (Warmup)
Chain 2: Iteration:  400 / 2000 [ 20%]  (Warmup)
Chain 2: Iteration:  600 / 2000 [ 30%]  (Warmup)
Chain 2: Iteration:  800 / 2000 [ 40%]  (Warmup)
Chain 2: Iteration: 1000 / 2000 [ 50%]  (Warmup)
Chain 2: Iteration: 1001 / 2000 [ 50%]  (Sampling)
Chain 2: Iteration: 1200 / 2000 [ 60%]  (Sampling)
Chain 2: Iteration: 1400 / 2000 [ 70%]  (Sampling)
Chain 2: Iteration: 1600 / 2000 [ 80%]  (Sampling)
Chain 2: Iteration: 1800 / 2000 [ 90%]  (Sampling)
Chain 2: Iteration: 2000 / 2000 [100%]  (Sampling)
Chain 2: 
Chain 2:  Elapsed Time: 0.47 seconds (Warm-up)
Chain 2:                208.219 seconds (Sampling)
Chain 2:                208.689 seconds (Total)
Chain 2:

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 3).
Chain 3: 
Chain 3: Gradient evaluation took 4.6e-05 seconds
Chain 3: 1000 transitions using 10 leapfrog steps per transition would take 0.46 seconds.
Chain 3: Adjust your expectations accordingly!
Chain 3: 
Chain 3: 
Chain 3: Iteration:    1 / 2000 [  0%]  (Warmup)
Chain 3: Iteration:  200 / 2000 [ 10%]  (Warmup)
Chain 3: Iteration:  400 / 2000 [ 20%]  (Warmup)
Chain 3: Iteration:  600 / 2000 [ 30%]  (Warmup)
Chain 3: Iteration:  800 / 2000 [ 40%]  (Warmup)
Chain 3: Iteration: 1000 / 2000 [ 50%]  (Warmup)
Chain 3: Iteration: 1001 / 2000 [ 50%]  (Sampling)
Chain 3: Iteration: 1200 / 2000 [ 60%]  (Sampling)
Chain 3: Iteration: 1400 / 2000 [ 70%]  (Sampling)
Chain 3: Iteration: 1600 / 2000 [ 80%]  (Sampling)
Chain 3: Iteration: 1800 / 2000 [ 90%]  (Sampling)
Chain 3: Iteration: 2000 / 2000 [100%]  (Sampling)
Chain 3: 
Chain 3:  Elapsed Time: 0.522 seconds (Warm-up)
Chain 3:                207.839 seconds (Sampling)
Chain 3:                208.361 seconds (Total)
Chain 3:

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 4).
Chain 4: 
Chain 4: Gradient evaluation took 2.7e-05 seconds
Chain 4: 1000 transitions using 10 leapfrog steps per transition would take 0.27 seconds.
Chain 4: Adjust your expectations accordingly!
Chain 4: 
Chain 4: 
Chain 4: Iteration:    1 / 2000 [  0%]  (Warmup)
Chain 4: Iteration:  200 / 2000 [ 10%]  (Warmup)
Chain 4: Iteration:  400 / 2000 [ 20%]  (Warmup)
Chain 4: Iteration:  600 / 2000 [ 30%]  (Warmup)
Chain 4: Iteration:  800 / 2000 [ 40%]  (Warmup)
Chain 4: Iteration: 1000 / 2000 [ 50%]  (Warmup)
Chain 4: Iteration: 1001 / 2000 [ 50%]  (Sampling)
Chain 4: Iteration: 1200 / 2000 [ 60%]  (Sampling)
Chain 4: Iteration: 1400 / 2000 [ 70%]  (Sampling)
Chain 4: Iteration: 1600 / 2000 [ 80%]  (Sampling)
Chain 4: Iteration: 1800 / 2000 [ 90%]  (Sampling)
Chain 4: Iteration: 2000 / 2000 [100%]  (Sampling)
Chain 4: 
Chain 4:  Elapsed Time: 0.31 seconds (Warm-up)
Chain 4:                210.47 seconds (Sampling)
Chain 4:                210.78 seconds (Total)
Chain 4: 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Define the chunk size (adjust based on available memory)}
\NormalTok{chunk\_size }\OtherTok{\textless{}{-}} \DecValTok{50000}  
\NormalTok{num\_chunks }\OtherTok{\textless{}{-}} \FunctionTok{ceiling}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(analysis\_data\_test) }\SpecialCharTok{/}\NormalTok{ chunk\_size)}

\CommentTok{\# Initialize a vector to store predictions}
\NormalTok{predictions }\OtherTok{\textless{}{-}} \FunctionTok{vector}\NormalTok{(}\StringTok{"numeric"}\NormalTok{, }\FunctionTok{nrow}\NormalTok{(analysis\_data\_test))}

\CommentTok{\# Loop through each chunk and generate predictions}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_chunks) \{}
\NormalTok{  start }\OtherTok{\textless{}{-}}\NormalTok{ ((i }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{) }\SpecialCharTok{*}\NormalTok{ chunk\_size) }\SpecialCharTok{+} \DecValTok{1}
\NormalTok{  end }\OtherTok{\textless{}{-}} \FunctionTok{min}\NormalTok{(i }\SpecialCharTok{*}\NormalTok{ chunk\_size, }\FunctionTok{nrow}\NormalTok{(analysis\_data\_test))}

@@

\CommentTok{\# Calculate MAE and RMSE for model evaluation}
\NormalTok{mae }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\FunctionTok{abs}\NormalTok{(predictions }\SpecialCharTok{{-}}\NormalTok{ analysis\_data\_test}\SpecialCharTok{$}\NormalTok{price\_current))}
\NormalTok{rmse }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{((predictions }\SpecialCharTok{{-}}\NormalTok{ analysis\_data\_test}\SpecialCharTok{$}\NormalTok{price\_current)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}

\NormalTok{evaluation\_metrics }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
  \AttributeTok{Metric =} \FunctionTok{c}\NormalTok{(}\StringTok{"Mean Absolute Error (MAE)"}\NormalTok{, }\StringTok{"Root Mean Squared Error (RMSE)"}\NormalTok{),}
  \AttributeTok{Value =} \FunctionTok{c}\NormalTok{(}\FunctionTok{round}\NormalTok{(mae, }\DecValTok{2}\NormalTok{), }\FunctionTok{round}\NormalTok{(rmse, }\DecValTok{2}\NormalTok{))}
\NormalTok{)}

\CommentTok{\# Display the results table}
\FunctionTok{kable}\NormalTok{(evaluation\_metrics, }\AttributeTok{col.names =} \FunctionTok{c}\NormalTok{(}\StringTok{"Evaluation Metric"}\NormalTok{, }\StringTok{"Value"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Evaluation Metric & Value \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mean Absolute Error (MAE) & 6.90 \\
Root Mean Squared Error (RMSE) & 17.77 \\
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(evaluation\_metrics)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
                          Metric Value
1      Mean Absolute Error (MAE)  6.90
2 Root Mean Squared Error (RMSE) 17.77
\end{verbatim}

@@

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

>>>>

\title{My title\thanks{Code and data are available at:
\url{https://github.com/RohanAlexander/starter_folder}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Another author}
\date{November 14, 2024}

@@

For this study, we utilize data from Project Hammer, a Canadian
initiative designed to monitor grocery prices across major retailers in
Canada. The Project Hammer dataset was collected from eight prominent
Canadian grocery vendors---Voila, T\&T, Loblaws, No Frills, Metro,
Galleria, Walmart, and Save-On-Foods---between February 28, 2024, and
the latest available data load in the database {[}
citeProjectHammerData{]}. This dataset enables us to investigate price
fluctuations, identify pricing trends, and explore potential competitive
or collusive patterns within the Canadian grocery sector. Project Hammer
aims to support regulatory efforts by providing data on price
transparency, making it suitable for academic research and potential
legal analysis. Following data processing and cleaning procedures
outlined in Section 3.2, the dataset was structured to allow an analysis
of historical price changes and vendor-specific price patterns. The
dataset contains 1,996,969 rows and 5 columns, with variables capturing
product (product name), vendor\_name (name of the grocery retailer),
price\_current (current product price at the time of recording),
price\_old (previous recorded price for the product), and
price\_difference (difference between the current and old prices). Price
data is recorded in Canadian dollars and captures a broad range of
grocery items from various categories, including fresh produce, dairy,
pantry staples, and household items. To ensure the quality and
consistency of the data, we focused on removing missing values and
imputing outlier prices when necessary. For this analysis, we excluded
entries with extreme price fluctuations beyond three standard
deviations, as these could represent temporary discounts or data
recording anomalies. This cleaning process provides a balanced and
accurate reflection of grocery pricing, allowing for robust statistical
analysis on vendor-specific trends and average price comparisons across
product types. By narrowing the scope to recent data, Project Hammer's
dataset captures real-time fluctuations in grocery pricing, providing
timely insights into potential market dynamics and consumer price
impacts. The analysis allows for future investigation of temporal price
trends, vendor-based price differences, and, more broadly, consumer
affordability in a market facing rising cost-of-living pressures.

@@

\begin{itemize}
    \item $\beta_0$ is the intercept term, representing the baseline estimate of $price_{current}$
    \item $\beta_1$, $\beta_2$, and $\beta_3$ are the coefficients representing the effects of $price_{old}$, $vendor_{name}$ and $price_{difference}$ on $price_{current}$.
    \item $\sigma^2$represents the variance of the error term, capturing unexplained variability in current prices.
\end{itemize}

@@

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\#\#\# Read Data \#\#\#\#}
\CommentTok{\# Load only a sample of the data to reduce memory usage (e.g., 10\% of the dataset)}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{853}\NormalTok{)}

\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{fread}\NormalTok{(}\StringTok{"C:/Users/eliza/Downloads/hammer{-}3{-}compressed/cleaned\_price\_changes.csv"}\NormalTok{)}
\NormalTok{analysis\_data }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data[}\FunctionTok{sample}\NormalTok{(.N, }\AttributeTok{size =} \FloatTok{0.1} \SpecialCharTok{*}\NormalTok{ .N)]}

\CommentTok{\# Split data into training and testing sets}
\NormalTok{train\_indices }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{seq\_len}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(analysis\_data)), }\AttributeTok{size =} \FloatTok{0.8} \SpecialCharTok{*} \FunctionTok{nrow}\NormalTok{(analysis\_data))}
\NormalTok{analysis\_data\_train }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data[train\_indices]}
\NormalTok{analysis\_data\_test }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data[}\SpecialCharTok{{-}}\NormalTok{train\_indices]}

\DocumentationTok{\#\#\#\# Model Data \#\#\#\#}
\CommentTok{\# Define a Bayesian regression model to predict \textasciigrave{}price\_current\textasciigrave{} with fewer iterations and lighter priors}
\FunctionTok{library}\NormalTok{(rstanarm)}
\NormalTok{model }\OtherTok{\textless{}{-}} \FunctionTok{stan\_glm}\NormalTok{(}
  \AttributeTok{formula =}\NormalTok{ price\_current }\SpecialCharTok{\textasciitilde{}}\NormalTok{ price\_old }\SpecialCharTok{+} \FunctionTok{as.factor}\NormalTok{(vendor\_name) }\SpecialCharTok{+}\NormalTok{ price\_difference,}
  \AttributeTok{data =}\NormalTok{ analysis\_data\_train,}
  \AttributeTok{family =} \FunctionTok{gaussian}\NormalTok{(),}
  \AttributeTok{prior =} \FunctionTok{normal}\NormalTok{(}\AttributeTok{location =} \DecValTok{0}\NormalTok{, }\AttributeTok{scale =} \DecValTok{5}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),      }\CommentTok{\# Slightly broader prior}
  \AttributeTok{prior\_intercept =} \FunctionTok{normal}\NormalTok{(}\AttributeTok{location =} \DecValTok{0}\NormalTok{, }\AttributeTok{scale =} \DecValTok{5}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),}
  \AttributeTok{prior\_aux =} \FunctionTok{exponential}\NormalTok{(}\AttributeTok{rate =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{autoscale =} \ConstantTok{TRUE}\NormalTok{),          }\CommentTok{\# Less informative prior}
  \AttributeTok{iter =} \DecValTok{500}\NormalTok{,                                                     }\CommentTok{\# Reduce iterations}
  \AttributeTok{chains =} \DecValTok{2}\NormalTok{,                                                     }\CommentTok{\# Fewer chains for faster computation}
  \AttributeTok{seed =} \DecValTok{853}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 1).
Chain 1: 
Chain 1: Gradient evaluation took 0.000105 seconds
Chain 1: 1000 transitions using 10 leapfrog steps per transition would take 1.05 seconds.
Chain 1: Adjust your expectations accordingly!
Chain 1: 
Chain 1: 
Chain 1: Iteration:   1 / 500 [  0%]  (Warmup)
Chain 1: Iteration:  50 / 500 [ 10%]  (Warmup)
Chain 1: Iteration: 100 / 500 [ 20%]  (Warmup)
Chain 1: Iteration: 150 / 500 [ 30%]  (Warmup)
Chain 1: Iteration: 200 / 500 [ 40%]  (Warmup)
Chain 1: Iteration: 250 / 500 [ 50%]  (Warmup)
Chain 1: Iteration: 251 / 500 [ 50%]  (Sampling)
Chain 1: Iteration: 300 / 500 [ 60%]  (Sampling)
Chain 1: Iteration: 350 / 500 [ 70%]  (Sampling)
Chain 1: Iteration: 400 / 500 [ 80%]  (Sampling)
Chain 1: Iteration: 450 / 500 [ 90%]  (Sampling)
Chain 1: Iteration: 500 / 500 [100%]  (Sampling)
Chain 1: 
Chain 1:  Elapsed Time: 0.056 seconds (Warm-up)
Chain 1:                3.902 seconds (Sampling)
Chain 1:                3.958 seconds (Total)
Chain 1:

SAMPLING FOR MODEL 'continuous' NOW (CHAIN 2).
Chain 2: 
Chain 2: Gradient evaluation took 2.5e-05 seconds
Chain 2: 1000 transitions using 10 leapfrog steps per transition would take 0.25 seconds.
Chain 2: Adjust your expectations accordingly!
Chain 2: 
Chain 2: 
Chain 2: Iteration:   1 / 500 [  0%]  (Warmup)
Chain 2: Iteration:  50 / 500 [ 10%]  (Warmup)
Chain 2: Iteration: 100 / 500 [ 20%]  (Warmup)
Chain 2: Iteration: 150 / 500 [ 30%]  (Warmup)
Chain 2: Iteration: 200 / 500 [ 40%]  (Warmup)
Chain 2: Iteration: 250 / 500 [ 50%]  (Warmup)
Chain 2: Iteration: 251 / 500 [ 50%]  (Sampling)
Chain 2: Iteration: 300 / 500 [ 60%]  (Sampling)
Chain 2: Iteration: 350 / 500 [ 70%]  (Sampling)
Chain 2: Iteration: 400 / 500 [ 80%]  (Sampling)
Chain 2: Iteration: 450 / 500 [ 90%]  (Sampling)
Chain 2: Iteration: 500 / 500 [100%]  (Sampling)
Chain 2: 
Chain 2:  Elapsed Time: 0.036 seconds (Warm-up)
Chain 2:                3.936 seconds (Sampling)
Chain 2:                3.972 seconds (Total)
Chain 2: 
\end{verbatim}

\begin{verbatim}
Warning: There were 1 chains where the estimated Bayesian Fraction of Missing Information was low. See
https://mc-stan.org/misc/warnings.html#bfmi-low
\end{verbatim}

\begin{verbatim}
Warning: Examine the pairs() plot to diagnose sampling problems
\end{verbatim}

\begin{verbatim}
Warning: The largest R-hat is 1.6, indicating chains have not mixed.
Running the chains for more iterations may help. See
https://mc-stan.org/misc/warnings.html#r-hat
\end{verbatim}

\begin{verbatim}
Warning: Bulk Effective Samples Size (ESS) is too low, indicating posterior means and medians may be unreliable.
Running the chains for more iterations may help. See
https://mc-stan.org/misc/warnings.html#bulk-ess
\end{verbatim}

\begin{verbatim}
Warning: Tail Effective Samples Size (ESS) is too low, indicating posterior variances and tail quantiles may be unreliable.
Running the chains for more iterations may help. See
https://mc-stan.org/misc/warnings.html#tail-ess
\end{verbatim}

\begin{verbatim}
Warning: Markov chains did not converge! Do not analyze results!
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\#\#\# Predict in Chunks \#\#\#\#}
\CommentTok{\# Define chunk size based on available memory}
\NormalTok{chunk\_size }\OtherTok{\textless{}{-}} \DecValTok{20000}  \CommentTok{\# Adjusted smaller chunk size for efficiency}
\NormalTok{num\_chunks }\OtherTok{\textless{}{-}} \FunctionTok{ceiling}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(analysis\_data\_test) }\SpecialCharTok{/}\NormalTok{ chunk\_size)}

\CommentTok{\# Initialize a vector to store predictions}
\NormalTok{predictions }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(analysis\_data\_test))}

\CommentTok{\# Loop through each chunk to generate predictions}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \FunctionTok{seq\_len}\NormalTok{(num\_chunks)) \{}
\NormalTok{  start }\OtherTok{\textless{}{-}}\NormalTok{ ((i }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{) }\SpecialCharTok{*}\NormalTok{ chunk\_size) }\SpecialCharTok{+} \DecValTok{1}
\NormalTok{  end }\OtherTok{\textless{}{-}} \FunctionTok{min}\NormalTok{(i }\SpecialCharTok{*}\NormalTok{ chunk\_size, }\FunctionTok{nrow}\NormalTok{(analysis\_data\_test))}

@@

\DocumentationTok{\#\#\#\# Model Evaluation Metrics \#\#\#\#}
\CommentTok{\# Calculate Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE)}
\NormalTok{mae }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\FunctionTok{abs}\NormalTok{(predictions }\SpecialCharTok{{-}}\NormalTok{ analysis\_data\_test}\SpecialCharTok{$}\NormalTok{price\_current))}
\NormalTok{rmse }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{((predictions }\SpecialCharTok{{-}}\NormalTok{ analysis\_data\_test}\SpecialCharTok{$}\NormalTok{price\_current)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}

\CommentTok{\# Store results in a data frame}
\NormalTok{evaluation\_metrics }\OtherTok{\textless{}{-}} \FunctionTok{data.table}\NormalTok{(}
  \AttributeTok{Metric =} \FunctionTok{c}\NormalTok{(}\StringTok{"Mean Absolute Error (MAE)"}\NormalTok{, }\StringTok{"Root Mean Squared Error (RMSE)"}\NormalTok{),}
  \AttributeTok{Value =} \FunctionTok{c}\NormalTok{(}\FunctionTok{round}\NormalTok{(mae, }\DecValTok{2}\NormalTok{), }\FunctionTok{round}\NormalTok{(rmse, }\DecValTok{2}\NormalTok{))}
\NormalTok{)}

\CommentTok{\# Display the results table}
\FunctionTok{print}\NormalTok{(evaluation\_metrics)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
                           Metric Value
                           <char> <num>
1:      Mean Absolute Error (MAE)  6.74
2: Root Mean Squared Error (RMSE) 17.98
\end{verbatim}

@@
